### 2021-02-22 papers/thesis/full/ch2-spherical-harmonics/spherical-harmonics.tex
Further edits. Need to type up proof of VSH x,y,z mults

First though, we require a few results concerning the incrementing and decrementing of the parameters for the Jacobi polynomials, and the three-term recurrence for the Jacobi polynomials, that will also prove useful later on in this chapter.
\begin{lemma}
	Let $\alpha, \beta \in \R$ be general parameters. Let $z \in [-1,1]$ and define $P_{-2}^{(\alpha+1, \beta+1)}(z) \equiv P_{-1}^{(\alpha+1, \beta+1)}(z) \equiv 0$. Then, for any $n \in \N_0$:
\bseqn{
	P_{n}^{(\alpha, \beta)}(z) =
		{1 \over 2n + \alpha + \beta + 1} \Big\{ & {(n+\alpha+\beta+1)(n+\alpha+\beta+2) \over 2n+\alpha+\beta+2} \: P_{n}^{(\alpha+1, \beta+1)}(z) \\
									  & + \big[{(n+\alpha+\beta+1)(n+\alpha) \over 2n+\alpha+\beta} \\
									  		& \quad \quad - {(n+\alpha+\beta+1)(n+\beta+1) \over 2n+\alpha+\beta+2}\big] \: P_{n-1}^{(\alpha+1, \beta+1)}(z) \\
									  & + {(n+\alpha)(n+\beta) \over 2n+\alpha+\beta} \: P_{n-2}^{(\alpha+1, \beta+1)}(z) \Big\}, \\
	P_{n}^{(\alpha, \beta)}(z) =
		{1 \over 2n + \alpha + \beta + 1} \Big\{ & {(n+\alpha+\beta+1)(n+\alpha+\beta+2) \over 2n+\alpha+\beta+2} \: P_{n}^{(\alpha+1, \beta+1)}(z) \\
									  & + \big[{(n+\alpha+\beta+1)(n+\alpha) \over 2n+\alpha+\beta} \\
									  		& \quad \quad - {(n+\alpha+\beta+1)(n+\beta+1) \over 2n+\alpha+\beta+2}\big] \: P_{n-1}^{(\alpha+1, \beta+1)}(z) \\
									  & + {(n+\alpha)(n+\beta) \over 2n+\alpha+\beta} \: P_{n-2}^{(\alpha+1, \beta+1)}(z) \Big\}, \\
	z \, P_{n}^{(\alpha, \beta)}(z) = 
		\Big\{ & {2(n+\alpha)(n+\beta) \over (2n + \alpha + \beta)(2n + \alpha + \beta + 1)} \: P_{n-1}^{(\alpha, \beta)}(z) \\
			 & {(\beta^2 - \alpha^2) \over (2n + \alpha + \beta)(2n + \alpha + \beta + 2)} \: P_{n}^{(\alpha, \beta)}(z) \\
			 & {2(n+1)(n + \alpha + \beta + 1) \over 2(2n + \alpha + \beta + 1)(2n + \alpha + \beta + 2)} \: P_{n+1}^{(\alpha, \beta)}(z).
}
\end{lemma}
\begin{proof}
	\bstodoinline{Do the second result (i.e. $(1-z^2)P_n$ relationship).}
	The first two results are simply consequences of the relationships established for incrementing and decrementing the parameters of Jacobi polynomials detailed in \cite[18.9.5, 18.9.6]{DLMF}, along with the symmetry relation that $P_{n}^{(\alpha, \beta)}(-z) \equiv (-1)^n P_{n}^{(\beta, \alpha)}(z)$. The final one is simply a rearranging of the established three-term recurrence detailed in \cite[18.9.1, 18.9.2]{DLMF}
\end{proof}
We thus can present a useful corollary specific for our needs.
\begin{corollary}\label{corollary:incrementjacparams}
	Let $l, m \in \N_0$ s.t. $0 \le m \le l$ and let $z \in [-1,1]$. Then:
\bseqn{
	(1-z^2) \, \jaclm{l}{m}(z) &=  \tilde \alpha_{l,m,1} P^{(m-1,m-1)}_{l-m}(z) + \tilde \alpha_{l,m,3} P^{(m-1,m-1)}_{l-m+2}(z) \\
	\jaclm{l}{m}(z) &= \tilde \alpha_{l,m,2} P^{(m+1,m+1)}_{l-m-2}(z) + \tilde \alpha_{l,m,4} P^{(m+1,m+1)}_{l-m}(z), \\
	z \, \jaclm{l}{m}(z) &= \tilde \gamma_{l,m,1} P^{(m,m)}_{l-m-1}(z) + \tilde \gamma_{l,m,2} P^{(m,m)}_{l-m+1}(z),
}
where
\bseqn{
	\tilde \alpha_{l,m,1} &:= {2l \over 2l+1} \\
	\tilde \alpha_{l,m,2} &:= 
		\begin{cases}
			- {l \over 2(2l+1)} \quad \text{if } l - m \ge 2 \\
			\quad \quad 0 \quad \quad \text{otherwise}
		\end{cases} \\
	\tilde \alpha_{l,m,3} &:= - {2(l-m+2)(l-m+1) \over (2l+1)(l+1)} \\
	\tilde \alpha_{l,m,4} &:= {(l+m+2)(l+m+1) \over 2(2l+1)(l+1)} \\
	\tilde \gamma_{l,m,1} &:= \begin{cases}
			\frac{l}{2l+1} \quad \text{if } l - m \ge 1 \\
			\quad 0 \quad \quad \text{otherwise}
		\end{cases} \\
	\tilde \gamma_{l,m,2} &:= \frac{(l-m+1)(l+m+1)}{(2l+1)(l+1)}.
}
\end{corollary}

\bsrefcor{corollary:incrementjacparams} allows us to easily determine the aforementioned coefficients, that we will formalise in the following Lemma.

@@

\begin{proof}
	The expression for multiplication of the spherical harmonic $\Ylm$ by $z$ is simply a consequence of the third result in \bsrefcor{corollary:incrementjacparams}:
\bseqn{
	z\,\Ylmxyz &= \clm \eimtheta \rho(z)^{|m|} z P^{(|m|,|m|)}_{l-|m|}(z)  \\
		     &= \clm \eimtheta \rho(z)^{|m|} \big[ \tilde \gamma_{l,m,1} P^{(|m|,|m|)}_{l-|m|-1}(z) + \tilde \gamma_{l,m,2} P^{(|m|,|m|)}_{l-|m|+1}(z) \big] \\
		     &= \gamma_{l,m,1} Y^{m}_{l-1}(x,y,z) + \gamma_{l,m,2} Y^{m}_{l+1}(x,y,z).
}

For multiplication by $x$ and $y$, note that the complex exponential satisfies
\bseqn{
	\costheta \, \eimtheta &= \frac{1}{2} (e^{i\theta} + e^{-i\theta}) \eimtheta =  \frac{1}{2} (e^{i(m+1)\theta} + e^{i(m-1)\theta}) \\
	\sintheta \, \eimtheta &= \frac{1}{2i} (e^{i\theta} - e^{-i\theta}) \eimtheta =  \frac{-i}{2} (e^{i(m+1)\theta} - e^{i(m-1)\theta})
}
Combining this with the results in \bsrefcor{corollary:incrementjacparams}, the expressions for multiplication of the spherical harmonic $\Ylm$ by $x$ and $y$ are then:
\bseqn{
	x \,\Ylmxyz &= \clm \costheta \: \eimtheta \: \rho(z)^{|m|+1} P^{(|m|,|m|)}_{l-|m|}(z) \\
	&= \half \clm (e^{i(m+1)\theta} + e^{i(m-1)\theta}) \rho(z)^{|m|+1} P^{(|m|,|m|)}_{l-|m|}(z) \\
	&= \half \clm e^{i(m+1)\theta} \rho(z)^{|m|+1} \: \big[ \tilde \alpha_{l,m,4} P^{(|m|+1,|m|+1)}_{l-|m|}(z) + \tilde \alpha_{l,m,2} P^{(|m|+1,|m|+1)}_{l-|m|-2}(z) \big] \\
	&\quad \quad + \half \clm e^{i(m-1)\theta} \rho(z)^{|m|-1} \: \big[ \tilde \alpha_{l,m,3} P^{(|m|-1,|m|-1)}_{l-|m|+2}(z) + \tilde \alpha_{l,m,1} P^{(|m|-1,|m|-1)}_{l-|m|}(z) \big] \\
	&= \alpha_{l,m,1} Y^{m-1}_{l-1}(x,y,z) +  \alpha_{l,m,2} Y^{m+1}_{l-1}(x,y,z) \\
	&\quad \quad + \alpha_{l,m,3} Y^{m-1}_{l+1}(x,y,z) + \alpha_{l,m,4} Y^{m+1}_{l+1}(x,y,z),
}
and
\bseqn{
	y \,\Ylmxyz &= \clm \sintheta \: \eimtheta \: \rho(z)^{|m|+1} P^{(|m|,|m|)}_{l-|m|}(z) \\
	&= -\half i \: \clm (e^{i(m+1)\theta} - e^{i(m-1)\theta}) \: \rho(z)^{|m|+1} P^{(|m|,|m|)}_{l-|m|}(z) \\
	&= i \: \Big\{ \alpha_{l,m,1} Y^{m-1}_{l-1}(x,y,z) - \alpha_{l,m,2} Y^{m+1}_{l-1}(x,y,z) \\
	&\quad \quad \quad + \alpha_{l,m,3} Y^{m-1}_{l+1}(x,y,z) - \alpha_{l,m,4} Y^{m+1}_{l+1}(x,y,z) \Big\}.
}
\end{proof}

@@

%%%
\section{Vector spherical harmonics as orthogonal vectors in three variables}

@@

% REMOVED SPIN harmonics and Clebsch Gorden coeff stuff as its much neater to use an inner product argument I have found.

@@

\begin{lemma}\label{lemma:VSHrecurrences}
	For $l \in \N$ and $m \in \Z$ s.t. $-l \le m \le l$, the vector spherical harmonics satisfy the relationships:
\bseqn{
	x \gradYlm &= A_{l,m,1} \gradY^{m-1}_{l-1} + A_{l,m,2} \gradY^{m+1}_{l-1} + A_{l,m,3} \gradY^{m-1}_{l+1} + A_{l,m,4} \gradY^{m+1}_{l+1} \\
& \quad \quad \quad + A_{l,m,5} \gradpY^{m-1}_{l} + A_{l,m,6} \gradpY^{m+1}_{l}, \\
	x \gradpYlm &= A_{l,m,1} \gradpY^{m-1}_{l-1} + A_{l,m,2} \gradpY^{m+1}_{l-1} + A_{l,m,3} \gradpY^{m-1}_{l+1} + A_{l,m,4} \gradpY^{m+1}_{l+1} \\
& \quad \quad \quad - A_{l,m,5} \gradY^{m-1}_{l} - A_{l,m,6} \gradY^{m+1}_{l}, \\
	y \gradYlm &= B_{l,m,1} \gradY^{m-1}_{l-1} + B_{l,m,2} \gradY^{m+1}_{l-1} + B_{l,m,3} \gradY^{m-1}_{l+1} + B_{l,m,4} \gradY^{m+1}_{l+1} \\
& \quad \quad \quad + B_{l,m,5} \gradpY^{m-1}_{l} + B_{l,m,6} \gradpY^{m+1}_{l}, \\
	y \gradpYlm &= B_{l,m,1} \gradpY^{m-1}_{l-1} + B_{l,m,2} \gradpY^{m+1}_{l-1} + B_{l,m,3} \gradpY^{m-1}_{l+1} + B_{l,m,4} \gradpY^{m+1}_{l+1} \\
& \quad \quad \quad - B_{l,m,5} \gradY^{m-1}_{l} - B_{l,m,6} \gradY^{m+1}_{l}, \\
	z \gradYlm &= \Gamma_{l,m,1} \gradY^{m}_{l-1} + \Gamma_{l,m,2} \gradY^{m}_{l+1} + \Gamma_{l,m,3} \gradpY^{m}_{l}, \\
	z \gradpYlm &= \Gamma_{l,m,1} \gradpY^{m}_{l-1} + \Gamma_{l,m,2} \gradpY^{m}_{l+1} - \Gamma_{l,m,3} \gradY^{m}_{l}
}
where,
\bseqn{
	A_{l,m,1} &:= {\clm c_{l-1}^{m-1} \over 2}
		\begin{cases}
			\tilde A_{l,m,1} & \text{if } m > 0 \\
			\tilde A_{l,\abs{m},2} & \text{if } m \le 0
		\end{cases} \\
	A_{l,m,2} &:= {\clm c_{l-1}^{m+1} \over 2}
		\begin{cases}
			\tilde A_{l,m,2} & \text{if } m \ge 0 \\
			\tilde A_{l,\abs{m},1} & \text{if } m < 0
		\end{cases} \\
	A_{l,m,3} &:= {\clm c_{l-1}^{m-1} \over 2}
		\begin{cases}
			\tilde A_{l,m,3} &\text{if } m > 0 \\
			\tilde A_{l,\abs{m},4} &\text{if } m \le 0
		\end{cases} \\
	A_{l,m,4} &:= {\clm c_{l-1}^{m+1} \over 2}
		\begin{cases}
			\tilde A_{l,m,4} &\text{if } m \ge 0 \\
			\tilde A_{l,\abs{m},3} &\text{if } m < 0
		\end{cases} \\
	A_{l,m,5} &:=
		\begin{cases}
			- i \: d_{l,m - 1} \: {c_l^{m-1} \over 2 \clm} &\text{if } m > 0 \\
			(-1)^m \: i \: d_{l,\abs{m}} \: {\clm \over 2 c_l^{m-1}} &\text{if } m \le 0
		\end{cases} \\
	A_{l,m,6} &:=
		\begin{cases}
			- i \: d_{l,m} \: {\clm \over 2 c_l^{m+1}} &\text{if } m \ge 0 \\
			(-1)^{m+1} \: i \: d_{l,\abs{m} - 1} \: {c_l^{m+1} \over 2 \clm} &\text{if } m < 0
		\end{cases} \\
	B_{l,m,j} &:= i (-1)^{j+1} A_{l,m,j} \quad \text{for } j = 1,\dots,6, \\
	\Gamma_{l,m,1} &:= \clm c_{l-1}^{m} \Big[ \abs{m}(\abs{m} + 2) {\tilde \gamma_{l,\abs{m},1} \over (c_{l-1}^{\abs{m}})^2} + d_{l,\abs{m}} d_{l-1,\abs{m}} {\tilde \gamma_{l,\abs{m}+1,1} \over (c_{l-1}^{\abs{m}+1})^2} \Big] \\
	\Gamma_{l,m,2} &:= \clm c_{l+1}^{m} \Big[ \abs{m}(\abs{m} + 2) {\tilde \gamma_{l,\abs{m},2} \over (c_{l+1}^{\abs{m}})^2} + d_{l,\abs{m}} d_{l+1,\abs{m}} {\tilde \gamma_{l,\abs{m}+1,2} \over (c_{l+1}^{\abs{m}+1})^2} \Big] \\
	\Gamma_{l,m,3} &:= (-1)^m \: i \: m
}
where the $c_{l'}^{m'}$, $d_{l',m'}$ are defined in \bsrefeqnslist{eqn:clmdef}{eqn:diffjac}{} respectively, and
\bseqn{
	\tilde A_{l,m,1} &:= \Big( (m^2 - 1) \mu_{l-1,m-1,2} - d_{l-1,m-1} \tilde \gamma_{l-1,m,2} \Big) {1 \over (\clm)^2} + d_{l,m} d_{l-1,m-1} {\mu_{l-1,m,2} \over (c_{l}^{m+1})^2} \\
	\tilde A_{l,m,2} &:= \Big( m(m+2) \mu_{l,m,1} - d_{l,m} \tilde \gamma_{l,m+1,1} \Big) {1 \over (c_{l-1}^{m+1})^2} + d_{l,m} d_{l-1,m+1} {\mu_{l,m+1,1} \over (c_{l-1}^{m+2})^2} \\
	\tilde A_{l,m,3} &:= \Big( (m^2 - 1) \mu_{l+1,m-1,1} - d_{l+1,m-1} \tilde \gamma_{l+1,m,1} \Big) {1 \over (\clm)^2} + d_{l,m} d_{l+1,m-1} {\mu_{l+1,m,1} \over (c_{l}^{m+1})^2} \\
	\tilde A_{l,m,4} &:= \Big( m(m+2) \mu_{l,m,2} - d_{l,m} \tilde \gamma_{l,m+1,2} \Big) {1 \over (c_{l+1}^{m+1})^2} + d_{l,m} d_{l+1,m+1} {\mu_{l,m+1,2} \over (c_{l+1}^{m+2})^2}.
}
\end{lemma}

>>>>

First though, we require a few results concerning the incrementing and decrementing of the parameters for the Jacobi polynomials, and the three-term recurrence for the Jacobi polynomials, that will also prove useful later on in this chapter.
\begin{lemma}
	Let $\alpha, \beta \in \R$ be general parameters. Let $z \in [-1,1]$ and define $P_{-2}^{(\alpha+1, \beta+1)}(z) \equiv P_{-1}^{(\alpha+1, \beta+1)}(z) \equiv 0$. Then, for any $n \in \N_0$:
\bseqn{
	P_{n}^{(\alpha, \beta)}(z) =
		{1 \over 2n + \alpha + \beta + 1} \Big\{ & - {(n+\alpha)(n+\beta) \over 2n+\alpha+\beta} \: P_{n-2}^{(\alpha+1, \beta+1)}(z) \\
									  & + (n+\alpha+\beta+1) \Big[{n+\alpha \over 2n+\alpha+\beta} - {n+\beta+1 \over 2n+\alpha+\beta+2}\Big] \: P_{n-1}^{(\alpha+1, \beta+1)}(z) \\
									  & {(n+\alpha+\beta+1)(n+\alpha+\beta+2) \over 2n+\alpha+\beta+2} \: P_{n}^{(\alpha+1, \beta+1)}(z) \Big\}, \\
	(1-z^2) \, P_{n}^{(\alpha, \beta)}(z) =
		{4 \over 2n + \alpha + \beta + 1} \Big\{ & + {(n+\alpha)(n+\beta) \over 2n+\alpha+\beta} \: P_{n}^{(\alpha-1, \beta-1)}(z) \\
									  & + (n+1) \Big[{n+\alpha+1 \over 2n+\alpha+\beta+2} - {n+\beta \over 2n+\alpha+\beta}\Big] \: P_{n+1}^{(\alpha-1, \beta-1)}(z) \\
									  & - {(n+1)(n+2) \over 2n+\alpha+\beta+2} \: P_{n+2}^{(\alpha-1, \beta-1)}(z) \Big\}, \\
	z \, P_{n}^{(\alpha, \beta)}(z) = 
		& {2(n+\alpha)(n+\beta) \over (2n + \alpha + \beta)(2n + \alpha + \beta + 1)} \: P_{n-1}^{(\alpha, \beta)}(z) \\
		& {(\beta^2 - \alpha^2) \over (2n + \alpha + \beta)(2n + \alpha + \beta + 2)} \: P_{n}^{(\alpha, \beta)}(z) \\
		& {2(n+1)(n + \alpha + \beta + 1) \over 2(2n + \alpha + \beta + 1)(2n + \alpha + \beta + 2)} \: P_{n+1}^{(\alpha, \beta)}(z).
}
\end{lemma}
\begin{proof}
	The first two results are simply consequences of the relationships established for incrementing and decrementing the parameters of Jacobi polynomials detailed in \cite[18.9.5, 18.9.6]{DLMF}, along with the symmetry relation that $P_{n}^{(\alpha, \beta)}(-z) \equiv (-1)^n P_{n}^{(\beta, \alpha)}(z)$. The final one is simply a rearranging of the established three-term recurrence detailed in \cite[18.9.1, 18.9.2]{DLMF}
\end{proof}
We thus can present a useful corollary specific for our needs.
\begin{corollary}\label{corollary:jacobirelations}
	Let $l, m \in \N_0$ s.t. $0 \le m \le l$ and let $z \in [-1,1]$. Then:
\bseqn{
	(1-z^2) \, \jaclm{l}{m}(z) &=  \tilde \alpha_{l,m,1} P^{(m-1,m-1)}_{l-m}(z) + \tilde \alpha_{l,m,3} P^{(m-1,m-1)}_{l-m+2}(z) \\
	\jaclm{l}{m}(z) &= \tilde \alpha_{l,m,2} P^{(m+1,m+1)}_{l-m-2}(z) + \tilde \alpha_{l,m,4} P^{(m+1,m+1)}_{l-m}(z), \\
	z \, \jaclm{l}{m}(z) &= \tilde \gamma_{l,m,1} P^{(m,m)}_{l-m-1}(z) + \tilde \gamma_{l,m,2} P^{(m,m)}_{l-m+1}(z),
}
where
\bseqn{
	\tilde \alpha_{l,m,1} &:= {2l \over 2l+1} \\
	\tilde \alpha_{l,m,2} &:= 
		\begin{cases}
			- {l \over 2(2l+1)} \quad \text{if } l - m \ge 2 \\
			\quad \quad 0 \quad \quad \text{otherwise}
		\end{cases} \\
	\tilde \alpha_{l,m,3} &:= - {2(l-m+2)(l-m+1) \over (2l+1)(l+1)} \\
	\tilde \alpha_{l,m,4} &:= {(l+m+2)(l+m+1) \over 2(2l+1)(l+1)} \\
	\tilde \gamma_{l,m,1} &:= \begin{cases}
			\frac{l}{2l+1} \quad \text{if } l - m \ge 1 \\
			\quad 0 \quad \quad \text{otherwise}
		\end{cases} \\
	\tilde \gamma_{l,m,2} &:= \frac{(l-m+1)(l+m+1)}{(2l+1)(l+1)}.
}
\end{corollary}

\bsrefcor{corollary:jacobirelations} allows us to easily determine the aforementioned coefficients, that we will formalise in the following Lemma.

@@

\begin{proof}
	The expression for multiplication of the spherical harmonic $\Ylm$ by $z$ is simply a consequence of the third result in \bsrefcor{corollary:jacobirelations}:
\bseqn{
	z\,\Ylmxyz &= \clm \eimtheta \rho(z)^{|m|} z P^{(|m|,|m|)}_{l-|m|}(z)  \\
		     &= \clm \eimtheta \rho(z)^{|m|} \big[ \tilde \gamma_{l,m,1} P^{(|m|,|m|)}_{l-|m|-1}(z) + \tilde \gamma_{l,m,2} P^{(|m|,|m|)}_{l-|m|+1}(z) \big] \\
		     &= \gamma_{l,m,1} Y^{m}_{l-1}(x,y,z) + \gamma_{l,m,2} Y^{m}_{l+1}(x,y,z).
}

For multiplication by $x$ and $y$, note that the complex exponential satisfies
\bseqn{
	\costheta \, \eimtheta &= \frac{1}{2} (e^{i\theta} + e^{-i\theta}) \eimtheta =  \frac{1}{2} (e^{i(m+1)\theta} + e^{i(m-1)\theta}) \\
	\sintheta \, \eimtheta &= \frac{1}{2i} (e^{i\theta} - e^{-i\theta}) \eimtheta =  \frac{-i}{2} (e^{i(m+1)\theta} - e^{i(m-1)\theta})
}
Combining this with the results in \bsrefcor{corollary:jacobirelations}, the expressions for multiplication of the spherical harmonic $\Ylm$ by $x$ and $y$ are then:
\bseqn{
	x \,\Ylmxyz &= \clm \costheta \: \eimtheta \: \rho(z)^{|m|+1} P^{(|m|,|m|)}_{l-|m|}(z) \\
	&= \half \clm (e^{i(m+1)\theta} + e^{i(m-1)\theta}) \rho(z)^{|m|+1} P^{(|m|,|m|)}_{l-|m|}(z) \\
	&= \half \clm e^{i(m+1)\theta} \rho(z)^{|m|+1} \: \big[ \tilde \alpha_{l,m,4} P^{(|m|+1,|m|+1)}_{l-|m|}(z) + \tilde \alpha_{l,m,2} P^{(|m|+1,|m|+1)}_{l-|m|-2}(z) \big] \\
	&\quad \quad + \half \clm e^{i(m-1)\theta} \rho(z)^{|m|-1} \: \big[ \tilde \alpha_{l,m,3} P^{(|m|-1,|m|-1)}_{l-|m|+2}(z) + \tilde \alpha_{l,m,1} P^{(|m|-1,|m|-1)}_{l-|m|}(z) \big] \\
	&= \alpha_{l,m,1} Y^{m-1}_{l-1}(x,y,z) +  \alpha_{l,m,2} Y^{m+1}_{l-1}(x,y,z) \\
	&\quad \quad + \alpha_{l,m,3} Y^{m-1}_{l+1}(x,y,z) + \alpha_{l,m,4} Y^{m+1}_{l+1}(x,y,z),
}
and
\bseqn{
	y \,\Ylmxyz &= \clm \sintheta \: \eimtheta \: \rho(z)^{|m|+1} P^{(|m|,|m|)}_{l-|m|}(z) \\
	&= -\half i \: \clm (e^{i(m+1)\theta} - e^{i(m-1)\theta}) \: \rho(z)^{|m|+1} P^{(|m|,|m|)}_{l-|m|}(z) \\
	&= i \: \Big\{ \alpha_{l,m,1} Y^{m-1}_{l-1}(x,y,z) - \alpha_{l,m,2} Y^{m+1}_{l-1}(x,y,z) \\
	&\quad \quad \quad + \alpha_{l,m,3} Y^{m-1}_{l+1}(x,y,z) - \alpha_{l,m,4} Y^{m+1}_{l+1}(x,y,z) \Big\}.
}
\end{proof}

@@

%%% TANGENT SPACE ----- VECTOR SHs
\section{Vector spherical harmonics as orthogonal vectors in three variables}

@@

@@

\begin{lemma}\label{lemma:VSHrecurrences}
	For $l \in \N$ and $m \in \Z$ s.t. $-l \le m \le l$, the vector spherical harmonics satisfy the relationships:
	x \gradYlm &= A_{l,m,1} \gradY^{m-1}_{l-1} + A_{l,m,2} \gradY^{m+1}_{l-1} + A_{l,m,3} \gradY^{m-1}_{l+1} + A_{l,m,4} \gradY^{m+1}_{l+1} \\
& \quad \quad \quad + A_{l,m,5} \gradpY^{m-1}_{l} + A_{l,m,6} \gradpY^{m+1}_{l}, \\
	x \gradpYlm &= A_{l,m,1} \gradpY^{m-1}_{l-1} + A_{l,m,2} \gradpY^{m+1}_{l-1} + A_{l,m,3} \gradpY^{m-1}_{l+1} + A_{l,m,4} \gradpY^{m+1}_{l+1} \\
& \quad \quad \quad - A_{l,m,5} \gradY^{m-1}_{l} - A_{l,m,6} \gradY^{m+1}_{l}, \\
	y \gradYlm &= B_{l,m,1} \gradY^{m-1}_{l-1} + B_{l,m,2} \gradY^{m+1}_{l-1} + B_{l,m,3} \gradY^{m-1}_{l+1} + B_{l,m,4} \gradY^{m+1}_{l+1} \\
& \quad \quad \quad + B_{l,m,5} \gradpY^{m-1}_{l} + B_{l,m,6} \gradpY^{m+1}_{l}, \\
	y \gradpYlm &= B_{l,m,1} \gradpY^{m-1}_{l-1} + B_{l,m,2} \gradpY^{m+1}_{l-1} + B_{l,m,3} \gradpY^{m-1}_{l+1} + B_{l,m,4} \gradpY^{m+1}_{l+1} \\
& \quad \quad \quad - B_{l,m,5} \gradY^{m-1}_{l} - B_{l,m,6} \gradY^{m+1}_{l}, \\
	z \gradYlm &= \Gamma_{l,m,1} \gradY^{m}_{l-1} + \Gamma_{l,m,2} \gradY^{m}_{l+1} + \Gamma_{l,m,3} \gradpY^{m}_{l}, \\
	z \gradpYlm &= \Gamma_{l,m,1} \gradpY^{m}_{l-1} + \Gamma_{l,m,2} \gradpY^{m}_{l+1} - \Gamma_{l,m,3} \gradY^{m}_{l}
where,
	A_{l,m,1} &:= {\clm c_{l-1}^{m-1} \over 2}
		\begin{cases}
			\tilde A_{l,m,1} & \text{if } m > 0 \\
			\tilde A_{l,\abs{m},2} & \text{if } m \le 0
		\end{cases} \\
	A_{l,m,2} &:= {\clm c_{l-1}^{m+1} \over 2}
		\begin{cases}
			\tilde A_{l,m,2} & \text{if } m \ge 0 \\
			\tilde A_{l,\abs{m},1} & \text{if } m < 0
		\end{cases} \\
	A_{l,m,3} &:= {\clm c_{l-1}^{m-1} \over 2}
		\begin{cases}
			\tilde A_{l,m,3} &\text{if } m > 0 \\
			\tilde A_{l,\abs{m},4} &\text{if } m \le 0
		\end{cases} \\
	A_{l,m,4} &:= {\clm c_{l-1}^{m+1} \over 2}
		\begin{cases}
			\tilde A_{l,m,4} &\text{if } m \ge 0 \\
			\tilde A_{l,\abs{m},3} &\text{if } m < 0
		\end{cases} \\
	A_{l,m,5} &:=
		\begin{cases}
			- i \: d_{l,m - 1} \: {c_l^{m-1} \over 2 \clm} &\text{if } m > 0 \\
			(-1)^m \: i \: d_{l,\abs{m}} \: {\clm \over 2 c_l^{m-1}} &\text{if } m \le 0
		\end{cases} \\
	A_{l,m,6} &:=
		\begin{cases}
			- i \: d_{l,m} \: {\clm \over 2 c_l^{m+1}} &\text{if } m \ge 0 \\
			(-1)^{m+1} \: i \: d_{l,\abs{m} - 1} \: {c_l^{m+1} \over 2 \clm} &\text{if } m < 0
		\end{cases} \\
	B_{l,m,j} &:= i (-1)^{j+1} A_{l,m,j} \quad \text{for } j = 1,\dots,6, \\
	\Gamma_{l,m,1} &:= \clm c_{l-1}^{m} \Big[ \abs{m}(\abs{m} + 2) {\tilde \gamma_{l,\abs{m},1} \over (c_{l-1}^{\abs{m}})^2} + d_{l,\abs{m}} d_{l-1,\abs{m}} {\tilde \gamma_{l,\abs{m}+1,1} \over (c_{l-1}^{\abs{m}+1})^2} \Big] \\
	\Gamma_{l,m,2} &:= \clm c_{l+1}^{m} \Big[ \abs{m}(\abs{m} + 2) {\tilde \gamma_{l,\abs{m},2} \over (c_{l+1}^{\abs{m}})^2} + d_{l,\abs{m}} d_{l+1,\abs{m}} {\tilde \gamma_{l,\abs{m}+1,2} \over (c_{l+1}^{\abs{m}+1})^2} \Big] \\
	\Gamma_{l,m,3} &:= (-1)^m \: i \: m
where the $c_{l'}^{m'}$, $d_{l',m'}$, $\tilde \gamma_{l',m',j}$ are defined in \bsrefeqn{eqn:clmdef}, \bsrefeqn{eqn:diffjac} and \bsrefcor{corollary:jacobirelations} respectively, and
	\tilde A_{l,m,1} &:= \Big( (m^2 - 1) \tilde \alpha_{l-1,m-1,4} - d_{l-1,m-1} \tilde \gamma_{l-1,m,2} \Big) {1 \over (\clm)^2} + d_{l,m} d_{l-1,m-1} {\tilde \alpha_{l,m+1,1} \over (c_{l-1}^{m})^2} \\
	\tilde A_{l,m,2} &:= \Big( m(m+2) \tilde \alpha_{l,m,2} - d_{l,m} \tilde \gamma_{l,m+1,1} \Big) {1 \over (c_{l-1}^{m+1})^2} + d_{l,m} d_{l-1,m+1} {\tilde \alpha_{l-1,m+2,3} \over (c_{l}^{m+1})^2} \\
	\tilde A_{l,m,3} &:= \Big( (m^2 - 1) \tilde \alpha_{l+1,m-1,2} - d_{l+1,m-1} \tilde \gamma_{l+1,m,1} \Big) {1 \over (\clm)^2} + d_{l,m} d_{l+1,m-1} {\tilde \alpha_{l,m+1,3} \over (c_{l+1}^{m})^2} \\
	\tilde A_{l,m,4} &:= \Big( m(m+2) \tilde \alpha_{l,m,4} - d_{l,m} \tilde \gamma_{l,m+1,2} \Big) {1 \over (c_{l+1}^{m+1})^2} + d_{l,m} d_{l+1,m+1} {\tilde \alpha_{l+1,m+2,1} \over (c_{l}^{m+1})^2}.
where again the $\tilde \alpha_{l',m',j}$ are defined in \bsrefcor{corollary:jacobirelations} too.
\end{lemma}
